%Introduction
\chapter{Introduction}

\section{Motivation}
Larger models, end of Moore's Law

\section{Forms of Parallelism}
Different forms of parallelism: thread, instruction level, data.

\section{Target Use Cases}
The two major use cases: one large model split up, a multi-domain (national-scale) model. Running on a local machine/laptop, deploying to a supercomputer.

\section{Requirements}
Requirements from user perspective. Requirements from developer's perspective.

\section{Parallelization Strategy}
Describes how we are going to implement parallelization in MODFLOW 6.

%Design Overview
\chapter{Design Overview}

\section{Application Structure}
Creation. Creation++: the interfaces. Assembly. Solution.
\section{Parallel Simulation}
This should describe a parallel simulation in terms of interdependence and timing of components.
\section{Input/Output Data}


%Advanced Exchanges
\chapter{Advanced Exchanges}

\begin{itemize}
\item discuss approach vs. traditional halo exchange
\end{itemize}
\section{Construction}
Halo construction, Grid builder, ...
\section{Interface Model}
\section{Timely Synchronization}

%Virtual Data
\chapter{Virtual Data}

\section{Layout}
\section{Run Control}
\section{Message Passing with MPI}

%Parallel Solution
\chapter{Parallel Solution}

\section{Extending Numerical Solution}
\section{PETSc Solver}
\section{Validation}
How does a parallel solution compare to the serial case?

%Parallel Development
\chapter{Parallel Development}

\section{Adding a Model or Package}

%Test Framework
\chapter{Test Framework}

Describes autotest framework for parallel. Guidelines what to test for.

%Outlook
\chapter{Outlook}

\section{Future Extensions}
Make classic exchanges parallel too.